Plug-and-play dual-tree algorithm runtime analysis

### 2015-10-31 bounds-files/sec01-supporting-lemmas.tex
Final little changes requested by reviewers.

\begin{lemma}
Consider a dataset $S$ with expansion constant $c$ and a subset $C \subseteq S$
such that every point in $C$ is separated by $\delta$.  Then, for any point
$p$ (which may or may not be in $S$), and any radius $\rho \delta > 0$:
\begin{equation}
| B_S(p, \rho \delta) \cap C | \le c^{2 + \lceil \log_2 \rho \rceil}.
\end{equation}
\label{lem:packing}
\end{lemma}

>>>>

\begin{lemma}
Consider a dataset $S$ with expansion constant $c$ and a subset $C \subseteq S$
such that every two distinct points in $C$ are separated by at least $\delta$.
Then, for any point $p$ (which may or may not be in $S$), and any radius $\rho
\delta > 0$:
\begin{equation}
| B_S(p, \rho \delta) \cap C | \le c^{2 + \lceil \log_2 \rho \rceil}.
\end{equation}
\label{lem:packing}
\end{lemma}
